# Introduction {#intro}

This is an introduction of the Value chain Hacker infrastructure;

Quick overview;

```{mermaid}
flowchart LR
  A[Hard edge] --> B(Round edge)
  B --> C{Decision}
  C --> D[Result one]
  C --> E[Result two]
```

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
# Install required packages for Bookdown and Quarto
install.packages(c(
  # Core packages for Bookdown and Quarto
  "bookdown", "rmarkdown", "knitr",
  
  # Core visualization libraries
  "ggplot2", "plotly", "lattice", "gridExtra", "cowplot", "patchwork",
  
  # Extended visualization and statistical analysis
  "ggpubr", "ggstatsplot", "PerformanceAnalytics", "Hmisc", 
  "corrplot", "ggcorrplot", "diagram", "igraph", "ggraph",
  
  # Tables and formatting
  "kableExtra", "xtable", "flextable", "DT", "formattable",
  
  # Data manipulation and analysis
  "dplyr", "tidyr", "data.table", "tibble", "forcats",
  
  # Spatial and interactive plotting
  "sf", "leaflet", "tmap", "maps", "mapview",
  
  # Network and graph visualizations
  "visNetwork", "networkD3", "sna", "Rgraphviz",
  
  # Quarto-specific enhancements
  "pagedown", "tinytex", "reticulate", "bslib", "thematic", "shiny"
))

# Install TinyTeX for PDF rendering in both Bookdown and Quarto
tinytex::install_tinytex()

# Reminder: Quarto itself needs to be installed separately from https://quarto.org/
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
