--- 
title: "A Minimal Book Example"
author: "Yihui Xie"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$. This is a test

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages(c("bookdown", "rmarkdown", "knitr", "ggplot2", "plotly", "lattice", "gridExtra", "cowplot", "patchwork", "ggpubr", "ggstatsplot", "PerformanceAnalytics", "Hmisc", "corrplot", "ggcorrplot", "diagram", "igraph", "ggraph", "kableExtra", "xtable", "flextable", "DT", "formattable", "dplyr", "tidyr", "data.table", "tibble", "forcats", "sf", "leaflet", "tmap", "maps", "mapview", "visNetwork", "networkD3", "sna", "Rgraphviz", "pagedown", "tinytex", "reticulate", "bslib", "thematic", "shiny", "quarto"))

# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
